### 2011-01-20 docs/runtime_parameters/runtime_parameters.tex
update

@@

@@

\verb=  cluster_min_width  = &   The minimum size on a side for a grid created using make\_new\_grids.  &  16 \\

@@

@@

@@

@@

\verb=  max_grid_size_base  = &   The largest grid size that will be created using make\_new\_grids for the coarsest level.  Defaults to {\tt max\_grid\_size}.  &  -1 \\

@@

\verb=  min_eff  = &   parameter for cluster algorithm for making new grids in adaptive problems  &  0.7d0 \\

@@

@@

@@

\verb=  plot_deltat  = &   rather than use a plot interva, plot a file after the solution has advanced past plot\_deltat in time  &  0.d0 \\

@@

@@

@@

\verb=  ppm_type  = &   0 = no ppm \newline 1 = 1985 ppm \newline 2 = 2009 ppm  &  1 \\

@@

>>>>

\verb=  bds_type  = &   0 = use ppm instead for multi-d integrator \newline 1 = bilinear  &  0 \\

@@

\verb=  blocking_factor  = &   grids must be an integer multiple of this number, if possible  &  8 \\

@@

@@

\verb=  drive_initial_convection  = &   freeze the temperature used in the reaction network to the initial value.  This is useful for developing an initial convective field to carry away the energy, while preventing the reactions from going nonlinear.  &  .false. \\
\verb=  dump_grid_file  = &    &  .false. \\

@@

\verb=  fix_base_state  = &   if true, don't call average to reset the base state at all, even during initialization  &  .false. \\

@@

\verb=  mach_max_abort  = &   maximum mach number before the code aborts  &  -1.d0 \\
\verb=  max_dt  = &   This is the maximum dt that is allowed  &  1.0d33 \\

@@

\verb=  max_grid_size_1  = &   The largest grid size that will be created using make\_new\_grids for the coarsest level.  Defaults to {\tt max\_grid\_size}.  &  -1 \\
\verb=  max_grid_size_2  = &   The largest grid size that will be created using make\_new\_grids for level 2 (the first refined level).  Defaults to {\tt max\_grid\_size}.  &  -1 \\
\verb=  max_grid_size_3  = &   The largest grid size that will be created using make\_new\_grids for level 3 (the second refined level) and beyond.  Defaults to {\tt max\_grid\_size}.  &  -1 \\

@@

\verb=  min_eff  = &   parameter for cluster algorithm for making new grids in adaptive problems  &  0.9d0 \\
\verb=  minwidth  = &   The minimum size on a side for a grid created using make\_new\_grids.  &  8 \\

@@

\verb=  nuclear_dt_fac  = &   If $T_{max}^n > T_{max}^{n-1}$ set the new dt =   min[dt, dt*{\tt nuclear\_dt\_fac}*( $T_{max}^{n-1}$ / $(T_{max}^n-T_{max}^{n-1})$ ) ] not checkpoint-compatible yet since it wouldn't be backwards compatible  &  -1.0d0 \\

@@

\verb=  plot_Hnuc  = &   plot nuclear energy generation rate (Hnuc) in plotfile  &  .true. \\
\verb=  plot_ad_excess  = &   plot the adiabatic excess  &  .false. \\

@@

\verb=  plot_cs  = &   plot soundspeed  &  .false. \\
\verb=  plot_deltat  = &   rather than use a plot interval, plot a file after the solution has advanced past plot\_deltat in time  &  -1.d0 \\

@@

\verb=  plot_gpi  = &   plot pi and grad(pi)  &  .true. \\
\verb=  plot_h_with_use_tfromp  = &   Turn on storing of enthalpy-based quantities in the plotfile when we are running with {\tt use\_tfromp}  &  .true. \\

@@

\verb=  plot_sponge_fdamp  = &   plot fdamp rather than sponge assumes sponge has the form 1/(1+dt*{\tt sponge\_kappa}*fdamp)  &  .false. \\

@@

\verb=  ppm_type  = &   0 = no ppm \newline 1 = 1985 ppm \newline 2 = Hybrid Sekora/Colella McCorquodale Colella 2009/2010 ppm  &  1 \\

@@

\verb=  restart_with_vel_field  = &   restart the simulation using a result from a {\tt drive\_initial\_convection} = T run note that this uses the restart variable to specify which file to restart from.  After reading in the velocity information from the restart file, the time and timestep number are zeroed.  &  .false. \\
